### 2020-09-28 prf/thm-pgv-closed-progress-confs.tex
Finished proofs. Now time for a consistency pass.

    We cannot have $\tm{L}=\tm{L'}$, otherwise the action on $\tm{y'}$ would be guarded by the action on $\tm{y}$, requiring $\pr(\ty{\co{S}})<\pr(\ty{S})$. The term $\tm{L'}$ must be ready to act on $\tm{y'}$, otherwise the action $\tm{y'}$ would be guarded by another action with priority smaller than $\pr{(\ty{S})}$, which contradicts our choice of $\tm{L}$ as having the smallest priority. Therefore, we have two terms ready to act on dual endpoints. We apply the appropriate reduction rule, \ie \LabTirName{E-Send} or \LabTirName{E-Close}.
  \item
    $\tm{L'}=\tm{N}$ and is a value. We rewrite $\tm{\conf{C}}$ to put $\tm{L}$ in the position corresponding to the endpoint it is blocked on, using \LabTirName{SC-ParComm}, \LabTirName{SC-ParAssoc}, and optionally \LabTirName{SC-ResSwap}. We then repeat the steps above with the term with the next smallest priority, until either we find a reduction, or the configuration has reached the desired normal form. (The argument based on the priority being the smallest continues to hold, since we know that neither $\tm{L}$ nor $\tm{L'}$ will be chosen, and no other term uses $\tm{y}$ or $\tm{y'}$.)
  \end{itemize} 
\end{proof}

>>>>

    We cannot have $\tm{L}=\tm{L'}$, otherwise the action on $\tm{y'}$ would be guarded by the action on $\tm{y}$, requiring $\pr(\ty{\co{S}})<\pr(\ty{S})$. The term $\tm{L'}$ must be ready to act on $\tm{y'}$, otherwise the action $\tm{y'}$ would be guarded by another action with priority smaller than $\pr{(\ty{S})}$, which contradicts our choice of $\tm{L}$ as having the smallest priority. Therefore, we have two terms ready to act on dual endpoints. We apply the appropriate reduction rule, \ie \LabTirName{E-Send} or \LabTirName{E-Close}.
  \item
    $\tm{L'}=\tm{N}$ and is a value. We rewrite $\tm{\conf{C}}$ to put $\tm{L}$ in the position corresponding to the endpoint it is blocked on, using \LabTirName{SC-ParComm}, \LabTirName{SC-ParAssoc}, and optionally \LabTirName{SC-ResSwap}. We then repeat the steps above with the term with the next smallest priority, until either we find a reduction, or the configuration has reached the desired normal form. (The argument based on the priority being the smallest continues to hold, since we know that neither $\tm{L}$ nor $\tm{L'}$ will be picked, and no other term uses $\tm{y}$ or $\tm{y'}$.)
  \end{itemize} 
\end{proof}

### 2020-09-28 priority-gv.tex
Finished proofs. Now time for a consistency pass.

\begin{definition}[Actions]
  \label{def:pgv-actions}
  A~term acts on an endpoint $\tm{x}$ if it is in one of the following forms:
  \begin{multicols}{3}
    \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
    \item $\tm{\link\;\pair{x}{y}}$ 
    \item $\tm{\link\;\pair{y}{x}}$
    \item $\tm{\send\;\pair{V}{x}}$
    \item $\tm{\recv\;{x}}$
    \item $\tm{\close\;{x}}$
    \item $\tm{\wait\;{x}}$
    \end{itemize}
  \end{multicols}
  \noindent
  A~term is an action if it acts on some endpoint $\tm{x}$.
\end{definition}

\begin{definition}[Ready Terms]
  \label{def:pgv-ready-actions}
  A~term $\tm{L}$ is ready if it is of the form $\tm{\plug{E}{M}}$, where $\tm{M}=\tm{\new}$, $\tm{M}=\tm{\spawn\;N}$, or $\tm{M}$ acts on $\tm{x}$. In the latter case, we say that $\tm{L}$ is ready to act on $\tm{x}$.
\end{definition}

\begin{restatablelemma}{lempgvreadypriority}
  \label{lem:pgv-ready-priority}
  If $\tseq[\cs{p}]{\ty{\Gamma}}{M}{T}$ is ready, then $\cs{p}=\cs{o}$ for some priority $\cs{o}$.
\end{restatablelemma}
\begin{proof}
  \admit
\end{proof}

>>>>

\begin{definition}[Actions]
  \label{def:pgv-actions}
  A~term acts on an endpoint $\tm{x}$ if it is of the form $\tm{\send\;\pair{V}{x}}$, $\tm{\recv\;{x}}$, $\tm{\close\;{x}}$, or $\tm{\wait\;{x}}$. A~term is an action if it acts on some endpoint $\tm{x}$.
\end{definition}

\begin{definition}[Ready Terms]
  \label{def:pgv-ready-actions}
  A~term $\tm{L}$ is ready if it is of the form $\tm{\plug{E}{M}}$, where $\tm{M}$ is of the form $\tm{\new}$, $\tm{\spawn\;N}$, $\tm{\link\;\pair{x}{y}}$ or $\tm{\link\;\pair{y}{x}}$, or $\tm{M}$ acts on $\tm{x}$. In the last case, we say that $\tm{L}$ is ready to act on $\tm{x}$.
\end{definition}

\begin{restatablelemma}{lempgvreadypriority}
  \label{lem:pgv-ready-priority}
  If $\tseq[\cs{p}]{\ty{\Gamma}}{L}{T}$ is ready to act on $\tmty{x}{S}\in\ty{\Gamma}$, then the priority bound $\cs{p}$ is some priority $\cs{o}$, \ie not $\cs{\pbot}$ or $\cs{\ptop}$.
\end{restatablelemma}
\begin{proof}
  Let $\tm{L}=\tm{\plug{E}{M}}$. By induction on the structure of $\tm{E}$. $\tm{M}$ has priority $\pr({\ty{S}})$, and each constructor of the evaluation context $\tm{E}$ passes on the \emph{maximum} of the priorities of its premises. No rule introduces the priority bound $\cs{\ptop}$ on the sequent.
\end{proof}
